Data Specialization for a Staged Lambda Calculus

### 2014-11-10 paper/semantics.tex
more minor fixes

We present an overview of the formal development along with our
terminology, as summarized in \figref{terminology}.

\figref{terminology}

@@

Since stage-1 evaluation does not evaluate stage-2 terms and since
stage-2 terms may be nested inside stage-1 terms, 1-evaluation cannot
reduce \lang\ terms to values.  Instead 1-evaluation yields a {\em
  partial value}, which which is a stage~\bbone\ term that have been
evaluated except for its stage-2 subterms, which can only
be~\bbtwo\ variables wrapped in $\next$ blocks.  \figref{validPvalues}
defines partial values.

@@

The relation 2-evaluation, defined by $\redtwosym$ judgment, as shows
in \figref{diaSemantics}, takes a stage \bbtwo\ term and reduces it to
a residual.  Apart from the evaluation of \prev\ and \pause, the
evaluation is straightforward. To reduce a \prev term, 2-evaluation
reduces the body by 1-evaluation to obtain a residual table and a
partial value.  It then reifies the residual table and the partial
value into an residual term, by creating for each variable-residual
pair in the table a corresponding variable binding in the residual,
finally ending with the partial value.

>>>>

We present an overview of the formal development along with our
terminology, as summarized in \ref{fig:termSplitSummary}.

\ref{fig:termSplitSummary}

@@

Since stage-1 evaluation does not evaluate stage-2 terms and since
stage-2 terms may be nested inside stage-1 terms, 1-evaluation cannot
reduce \lang\ terms to values.  Instead 1-evaluation yields a {\em
  partial value}, which which is a stage~\bbone\ term that have been
evaluated except for its stage-2 subterms, which can only
be~\bbtwo\ variables wrapped in $\next$ blocks.  \ref{fig:validPvalues}
defines partial values.

@@

The relation 2-evaluation, defined by $\redtwosym$ judgment, as shows
in \ref{fig:diaSemantics}, takes a stage \bbtwo\ term and reduces it to
a residual.  Apart from the evaluation of \prev\ and \pause, the
evaluation is straightforward. To reduce a \prev term, 2-evaluation
reduces the body by 1-evaluation to obtain a residual table and a
partial value.  It then reifies the residual table and the partial
value into an residual term, by creating for each variable-residual
pair in the table a corresponding variable binding in the residual,
finally ending with the partial value.
